Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-04-19 Paper/Manuscript.tex
Changes to TS(f) and Sv(f) for frequency parameter

The discrete Fourier transforms of the target signal, $\ypctargetf(\samplesymf)$, and the reduced auto correlation signal, $\ymfautoredf(\samplesymf)$, are given by:
\begin{eqnarray}
\label{eq:DFT_Target_Auto}
\ypctargetf(\samplesymf) & = & \dft_\ndft(\ypctarget(\samplesymt)),\\
\ymfautoredf(\samplesymf) & = & \dft_\ndft(\ymfautored(\samplesymt)),
\end{eqnarray}
where $\dft$ indicates the Fourier transform of length $\ndft$ and $\samplesymf$ the sample index in the frequency domain.
The nomalized discrete Fourier transform of the target signal, $\ypctargetnormf(\samplesymf)$, (Fig. \ref{fi:TS}) is then calculated by: 
%
\begin{equation}
\label{eq:DFT_Target_Auto_Norm}
\ypctargetnormf(\samplesymf) = \frac{\ypctargetf(\samplesymf)} {\ymfautoredf(\samplesymf)}.
\end{equation}
%
\hl{The corresponding frequencies f\_m\_t (?) are calculate as follows...

See the function EK80CalculationPaper.calcDFTforTS. Nils Olav did not quite get this so please enlighten me...}

@@

Target strength can then be estimated using Eq. \ref{eq:TS}, but with $\freqsym$ replaced by the discrete index of frequency, $\samplesymf$:
\begin{equation}
\label{eq:TS_f}
\ts(\samplesymf) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\samplesymf)\range_t 
- 10\log_{10}\left( \frac{\ptxe \wlen_\samplesymf^2 \gain^2(\along_t,\athw_t,f_\samplesymf)}{16\pi^2} \right).
\end{equation}
%
\begin{figure}
\includegraphics[width=16cm]{Fig_TS}
\caption{\label{fi:TS}The $\ypctargetf(\samplesymf)$ (upper), $\ymfautoredf(\samplesymf)$ (middle) and $\ypctargetnormf(\samplesymf)$ (lower).}
\end{figure}

@@

\hl{Comment from Nils Olav: Using $m$ as an argument to a function is not ideal. If we use the function argument perhaps using $f_m$ would be more logical, i.e. $\lambda(f_m)$. Alternatively using $lambda_m$ is possible. The latter is perhaps more in line with the code since the parameter is an array windexed with $m$ and not a function. $Psi(f)$, on the the other hand is derived from a function, see below.}

@@

\hl{TODO: Explain edge cases.}

@@

%
\hl{TODO: How to index samples along range? In the code \_n is used to indicate the range component of the FFt's. Needs attention.}

The normalized discrete Fourier transform of the windowed data, $\ypcvolumenormf(\samplesymf)$, is then given by:
%
\begin{equation}
\label{eq:FFT_volume_norm}
\ypcvolumenormf(\samplesymf) = \frac{\ypcvolumef(\samplesymf)}{\ymfautof(\samplesymf)},
\end{equation}
%
and received power into a matched load, $\prxevf(\samplesymf)$, is estimated from:
%
\begin{equation}
\label{eq:prx_FFT_volume}
\prxevf(\samplesymf) = \nchannels \left( \frac{|\ypcvolumenormf(\samplesymf)|}{2\sqrt{2}} \right)^2 \left( \frac{|\zrxe+\ztde|}{|\zrxe|}\right)^2 \\
\frac{1}{|\ztde|}. % All channels (*4), matched load (/2), and effective values (/sqrt(2))
\end{equation}
%
Finally, the discretized estimate of $\sv(\freqsym)$, $\sv(\samplesymf)$, is given by:
%
\begin{equation}
\label{eq:Sv_FFT}
\sv(\samplesymf) = 10\log_{10}(\prxevf(\samplesymf)) + 2\absorp(\samplesymf) \range_c \\
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\samplesymf) \cw \tslide \eqang(\samplesymf) \gainzero^2(\samplesymf) }{32\pi^2} \right).
\end{equation}

>>>>

The discrete Fourier transforms of the target signal, $\ypctargetf(\samplesymf)$, and the reduced auto correlation signal, $\ymfautoredf(\samplesymf)$, are given by:
\begin{eqnarray}
\label{eq:DFT_Target_Auto}
\ypctargetf(\samplesymf) & = & \dft_\ndft(\ypctarget(\samplesymt)),\\
\ymfautoredf(\samplesymf) & = & \dft_\ndft(\ymfautored(\samplesymt)),
\end{eqnarray}
where $\dft$ indicates the Fourier transform of length $\ndft$ and $\samplesymf$ the sample index in the frequency domain.
The nomalized discrete Fourier transform of the target signal, $\ypctargetnormf(\samplesymf)$, (Fig. \ref{fi:TS}) is then calculated by: 
%
\begin{equation}
\label{eq:DFT_Target_Auto_Norm}
\ypctargetnormf(\samplesymf) = \frac{\ypctargetf(\samplesymf)} {\ymfautoredf(\samplesymf)}.
\end{equation}

@@

Target strength can then be estimated using Eq. \ref{eq:TS}:
\begin{equation}
\label{eq:TS_f}
\ts(\freqsym) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\freqsym)\range_t - 10\log_{10}\left( \frac{\ptxe \wlen^2 \gain^2(\along_t,\athw_t,f)}{16\pi^2} \right)
\end{equation}
where the sample index $\samplesymf$ corresponding to frequency $\freqsym$ can be estimated using
\begin{equation}
\label{eq:m(f)}
\samplesymf = \lfloor \frac{\freqsym}{\fsdec} \ndft \rfloor \mod \ndft
\end{equation}
%
\begin{figure}
\includegraphics[width=16cm]{Fig_TS}
\caption{\label{fi:TS}The $\ypctargetf(\samplesymf)$ (upper), $\ymfautoredf(\samplesymf)$ (middle) and $\ypctargetnormf(\samplesymf)$ (lower).}
\end{figure}

@@

@@

@@

The normalized discrete Fourier transform of the windowed data, $\ypcvolumenormf(\samplesymf)$, is then given by:
%
\begin{equation}
\label{eq:FFT_volume_norm}
\ypcvolumenormf(\samplesymf) = \frac{\ypcvolumef(\samplesymf)}{\ymfautof(\samplesymf)},
\end{equation}
%
and received power into a matched load, $\prxevf(\samplesymf)$, is estimated from:
%
\begin{equation}
\label{eq:prx_FFT_volume}
\prxevf(\samplesymf) = \nchannels \left( \frac{|\ypcvolumenormf(\samplesymf)|}{2\sqrt{2}} \right)^2 \left( \frac{|\zrxe+\ztde|}{|\zrxe|}\right)^2 \\
\frac{1}{|\ztde|}. % All channels (*4), matched load (/2), and effective values (/sqrt(2))
\end{equation}
%
Finally, the discretized estimate of $\sv(\freqsym)$, $\sv(\samplesymf)$, is given by:

%
\begin{equation}
\label{eq:Sv_FFT}
\sv(\freqsym) = 10\log_{10}(\prxevf(\samplesymf)) + 2\absorp(\freqsym) \range_c - 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym) }{32\pi^2} \right).
\end{equation}
where the sample index $\samplesymf$ corresponding to frequency $\freqsym$ can be estimated using
\begin{equation}
\label{eq:m(f)}
\samplesymf = \lfloor \frac{\freqsym}{\fsdec} \ndft \rfloor \mod \ndft
\end{equation}
